An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-09 main.tex
Change plots for validation.
Not sure if I'm a fan.

Also, add some abbreviations.

To carry out this large numerical experiment, 164 strategies are used from
\cite{axelrodproject}. These include 161 default strategies in the library at
the time (excluding strategies classified as having a long run time and those
that make use of the length of the game) as well as
the following 3 finite state machine machine strategies \cite{Ashlock2006}:

% TODO Include details about the 3 extra FSM strategies.
% Possibly draw pictorial representations?
% Remove the FSM strategies if they don't perform well.

>>>>

To carry out this large numerical experiment, 164 strategies are used from
\cite{axelrodproject}. These include 161 default strategies in the library at
the time (excluding strategies classified as having a long run time and those
that make use of the length of the game) as well as
the following 6 finite state machine machine strategies \cite{Ashlock2006}:

% TODO Include details about the 3/6 extra FSM strategies.
% Possibly draw pictorial representations?
% Remove the FSM strategies if they don't perform well.
% TODO Decide if we include all 6 (so the same original 3 with the wrong initial
% state) in the entire analysis.
